Charity analysis

### 2022-07-21 Shiny/Test/Flexdashboard rows.Rmd
Changing a colour.

  # Creating the value box for administrative expenses
  output$KPI_box_admin <- renderValueBox({
    valueBox(
      value = KPI_admin(),
      caption = "Admin spend",
      color = met.brewer("Troy", n = 1),
      icon = "fa-random"
    )
  })

>>>>

  # Creating the value box for administrative expenses
  output$KPI_box_admin <- renderValueBox({
    valueBox(
      value = KPI_admin(),
      caption = "Admin spend",
      color = met.brewer("Wissing", n = 1),
      icon = "fa-random"
    )
  })
